---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nightvale

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/mcguinlu/nightvale/workflows/R-CMD-check/badge.svg)](https://github.com/mcguinlu/nightvale/actions)
<!-- badges: end -->

## Background

[Welcome to Night Vale](http://www.welcometonightvale.com/) is a twice-monthly podcast in the style of community updates for the small desert town of Night Vale, with heavy themes of surreal humor and horror. A key and recurring part of the show is "Today's Proverb". This package provides the metadata and proverb for each episode as a dataset, in addition to a function to return a nicely formatted proverb to the console.  

## Installation

This package is a GitHub only package, and can be installed using:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mcguinlu/nightvale")
```

## Usage

### Access the data

```{r eval=TRUE}
library(nightvale)

head(proverb_data)
```


### Get a random proverb

```{r eval=TRUE}
proverb()
```

### Get a specific proverb

```{r eval=TRUE}
proverb(22)
```

